A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-11 final project/Manuscript.Rmd
Updated literature review section of final paper

Participants used a variety of approaches in formulating their submissions including:

- Classification Trees with Bagging [@White];

- C4.5 [@Seewald];

- Evolutionary Algorithm [@Koudijs];

- Inductive Learning by Logic Minimization (ILLM) [@Gamberger];

- Mask Perceptron with Boosting [@Leckie];

- Naïve Bayes [@Elkan]; and

- Neural Networks[@Crocoll], [@Kim];

- Scoring System [@Lewandowski];

- Support Vector Machines; and

- XCS [@Greenyer].

@@

<!--
10 Gustavo Denicolay and Gaston Morales. CoIL Challenge 2000 Submission for the Description Task. [ps.gz] [pdf] - Not sure what they used

12 János Abonyi, Hans Roubos. A Simple Fuzzy Classifier based on Inconsistency Analysis of Labeled Data. [ps.gz],[pdf]

13 Jonathan Carter. Coil 2000 Challenge Submission: Genetic Algorithms and Hill-climbers. [ps.gz], [pdf]

14 Juha Vesanto and Janne Sinkkonen. Submission for the CoIL Challenge 2000. [ps.gz], [pdf]

15 Mark-André Krogel. A Data Mining Case Study. [ps.gz],[pdf]

16 Michel Bera and Bertrand Lamy. Kxen at CoIL Challenge 2000. [ps.gz], [pdf]

17 Paul Rickets. CoIL Challenge 2000 submission. [ps.gz], [pdf]

18 Petr Mikšovský, Jirí Klema. COIL Challenge 2000. [ps.gz], [pdf]

19 Petri Kontkanen. CoIL 2000 Submission. [ps.gz], [pdf]

20 Philip Brierley. COIL 2000 Challenge: Characteristics of caravan insurance policy owners. [ps.gz] [pdf]

21 Robert M. Simmonds. ACT Study report using Classification and Regression Tree (CART) Analysis. [ps.gz], [pdf]

22 S. Sathiya Keerthi and Chong Jin Ong. Solution of the CoIL Challenge 2000 Task Using Support Vector Machines. [ps.gz], [pdf]

23 Serhiy Shtovba, Yakiv Mashnitskiy. The Backpropagation Multilayer Feedforward Neural Network Based Competition Task Solution.

24 Serhiy Shtovba. Phase Intervals and Genetic Algorithms Based Competition Task Solution. [ps.gz], [pdf]

25 Jurgen A. Doornik and Steve Moyle. LOGIT Modelling. [ps.gz], [pdf]

26 Thomas Martini Jorgensen and Christian Linneberg. Subspace Projections – an approach to variable selection and modeling. [ps.gz], [pdf]

27 Tom McKone and Curt Stenger. COIL CHALLENGE 2000 Submission. [ps.gz], [pdf]

28 Tomislav Šmuc. COIL 2000 Challenge Solution based on ILLM-SG Methodology. [ps.gz], [pdf]

29 Uzay Kaymak and Magne Setnes. Target Selection based on fuzzy clustering: a volume prototype approach to CoIL Challenge 2000. [ps.gz], [pdf]

-->

@@

# Appendices

- Supplemental tables and/or figures.

## R statistical programming code.

>>>>

Participants used a variety of approaches in formulating their submissions including: Boosted Decision Tree [@McKone], Classification and Regressio Tree (CART) [@Simmonds], Classification Trees with Bagging [@White], C4.5 [@Rickets; @Seewald], Evolutionary Algorithm [@Koudijs], Fuzzy Classifier [@Abonyi; @Kaymak], Genetic Algorithms and Hill-climbers [@Carter], Inductive Learning by Logic Minimization (ILLM) [@Gamberger; @Smuc], Instance Based Reasoning (iBARET) [@Miksovsky], K-Means [@Vesanto], KXEN [@Bera], LOGIT [@Doornik], Mask Perceptron with Boosting [@Leckie], Midos Algorithm [@Krogel], N-Tuple Classifier [@Jorgensen], Naïve Bayes [@Elkan; @Kontkanen], Neural Networks[@Brierley; @Crocoll; @Kim; @Shtovba_Mashnitskiy], Phase Intervals and Genetic Algorithms [@Shtovba], Scoring System [@Lewandowski], Support Vector Machines[@Keerthi], and XCS [@Greenyer].

@@

@@

# Appendices
<!--
- Supplemental tables and/or figures.
-->
## R statistical programming code.

### 2019-11-11 final project/Manuscript.tex
Updated literature review section of final paper

Participants used a variety of approaches in formulating their submissions including:

\begin{itemize}
\item
  Classification Trees with Bagging (White \& Liu, 2000);
\item
  C4.5 (Seewald, 2000), (Rickets, 2000);
\item
  Evolutionary Algorithm (Koudijs, 2000);
\item
  Fuzzy Classifier (János Abonyi, 2000);
\item
  Genetic Algorithms and Hill-climbers (Carter, 2000);
\item
  Inductive Learning by Logic Minimization (ILLM) (Gamberger, 2000);
\item
  K-Means (Vesanto \& Sinkkonen, 2000);
\item
  KXEN (Bera \& Lamy, 2000);
\item
  Mask Perceptron with Boosting (Leckie \& Ferra, 2000);
\item
  Midos Algorithm (Krogel, 2000);
\item
  Naïve Bayes (Elkan, 2000); and
\item
  Neural Networks(Crocoll, 2000), (Kim \& Street, 2000);
\item
  Scoring System (Lewandowski, 2000);
\item
  Support Vector Machines; and
\item
  XCS (Greenyer, 2000).
\end{itemize}

@@

@@

@@

@@

@@

\leavevmode\hypertarget{ref-Putten}{}%
Putten, P., Ruiter, M., \& Someren, M. (2000). CoIL challenge 2000 tasks and results: Predicting and explaining caravan policy ownership.

@@

>>>>

Participants used a variety of approaches in formulating their submissions including: Boosted Decision Tree (McKone \& Stenger, 2000), Classification and Regressio Tree (CART) (Simmonds, 2000), Classification Trees with Bagging (White \& Liu, 2000), C4.5 (Rickets, 2000; Seewald, 2000), Evolutionary Algorithm (Koudijs, 2000), Fuzzy Classifier (János Abonyi, 2000; Kaymak \& Setnes, 2000), Genetic Algorithms and Hill-climbers (Carter, 2000), Inductive Learning by Logic Minimization (ILLM) (Gamberger, 2000; Šmuc, 2000), Instance Based Reasoning (iBARET) (Mikšovský \& Klema, 2000), K-Means (Vesanto \& Sinkkonen, 2000), KXEN (Bera \& Lamy, 2000), LOGIT (Doornik \& Moyle, 2000), Mask Perceptron with Boosting (Leckie \& Ferra, 2000), Midos Algorithm (Krogel, 2000), N-Tuple Classifier (Jorgensen \& Linneberg, 2000), Naïve Bayes (Elkan, 2000; Kontkanen, 2000), Neural Networks(Brierley, 2000; Crocoll, 2000; Kim \& Street, 2000; Shtovba \& Mashnitskiy, 2000), Phase Intervals and Genetic Algorithms (Shtovba, 2000), Scoring System (Lewandowski, 2000), Support Vector Machines(Keerthi \& Ong, 2000), and XCS (Greenyer, 2000).

@@

\leavevmode\hypertarget{ref-Brierley}{}%
Brierley, P. (2000). COIL 2000 challenge: Characteristics of caravan insurance policy owners. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/BRIERL~1.pdf}

@@

\leavevmode\hypertarget{ref-Doornik}{}%
Doornik, J. A., \& Moyle, S. (2000). LOGIT modelling. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/MOYLEP~1.pdf}

@@

\leavevmode\hypertarget{ref-Jorgensen}{}%
Jorgensen, T. M., \& Linneberg, C. (2000). Subspace projections -- an approach to variable selection and modeling. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/JORGEN~1.pdf}

\leavevmode\hypertarget{ref-Kaymak}{}%
Kaymak, U., \& Setnes, M. (2000). Target selection based on fuzzy clustering: A volume prototype approach to coil challenge 2000. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/KAYMAK~1.pdf}

\leavevmode\hypertarget{ref-Keerthi}{}%
Keerthi, S. S., \& Ong, C. J. (2000). Solution of the coil challenge 2000 task using support vector machines. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/KEERTH~1.pdf}

@@

\leavevmode\hypertarget{ref-Kontkanen}{}%
Kontkanen, P. (2000). CoIL 2000 submission. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/KONTKA~1.pdf}

@@

\leavevmode\hypertarget{ref-McKone}{}%
McKone, T., \& Stenger, C. (2000). COIL challenge 2000 submission. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/MCKONE~1.pdf}

\leavevmode\hypertarget{ref-Miksovsky}{}%
Mikšovský, P., \& Klema, J. (2000). CoIL challenge 2000. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/MIKSOV~1.pdf}

\leavevmode\hypertarget{ref-Putten}{}%
Putten, P., Ruiter, M., \& Someren, M. (2000). CoIL challenge 2000 tasks and results: Predicting and explaining caravan policy ownership. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf}

@@

\leavevmode\hypertarget{ref-Shtovba}{}%
Shtovba, S. (2000). Phase intervals and genetic algorithms based competition task solution. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/SHTOVB~2.pdf}

\leavevmode\hypertarget{ref-Shtovba_Mashnitskiy}{}%
Shtovba, S., \& Mashnitskiy, Y. (2000). The backpropagation multilayer feedforward neural network based competition task solution. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/SHTOVB~1.pdf}

\leavevmode\hypertarget{ref-Simmonds}{}%
Simmonds, R. M. (2000). ACT study report using classification and regression tree (cart) analysis. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/SIMMON~1.pdf}

\leavevmode\hypertarget{ref-Smuc}{}%
Šmuc, T. (2000). COIL 2000 challenge solution based on illm-sg methodology. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/SMUCPS~1.pdf}
